### 2019-03-24 Rapport/TG_ITA/Bibliographic_analysis/Coursera.tex
Assigment week 2

Learning rate
	how to choose: look graph min J vs No. of iterations. It should decrease at every iteration.

@@

>>>>

Vectorized implementation of Gradient descent $\mathcal{O}(n^{2})$
	\begin{equation}
	\theta := \theta - \frac{\alpha}{m} X^{T}(g(X\theta)-Y)	
		\end{equation}
Learning rate
	how to choose: look graph min J vs No. of iterations. It should decrease at every iteration.

@@

	\subsubsection{Week 3}

Classification problem: take a bunch of data and outputs discrete  values
	multi class: several discrete outcomes
	binary class: 2 outputs (0,1)

Logistic regression (classification algorithm): output is always between 0 and 1. sigmoid function or logistic function: $g(z) = \frac{1}{1+e^{-z}}$. Hypothesis: $h(x)=g(\theta^{T}x)$ maps any real number to the (0,l) interval. $h(x)$ will give the probability that our output is 1.

Decision boundary: line where the hypothesis equals to 0.5. Separates 2 regions, greater than and less than 0.5 to the hypothesis function. The decision boundaries can be linear or not.
	The decision boundary is a property of the hypothesis function. The greater the order of the polynomial, the more complex is the shape.

Cost function: find a function that is convex to arrive in a global minimum.

Optimization algorithms:
	\begin{itemize}
	\item Gradient descent
	\item Conjugate gradient
	\item BFGS
	\item L-BFGS
	\end{itemize}

No need to manually pick $\alpha$ in the 3 last algorithms. They are fasten than gradient descent. However, they are more complex

Multiclass classification
	One vs all (one vs rest)

Avoid overfitting: doesn't add too much features, otherwise the training data will not predict well values.	The cost function is almost zero to the training example.
	To fight this problem: reduce the number of features (select which features to keep), regularization (keep all features but reduce the magnitude of parameters theta), Regularization works well when we have a lot of slightly useful features.
	Add a regularization term in the end of the cost function. A regularization parameter is set to make a trade off between how well the data is fitted and weakening the parameters theta.

In the end we have a regularized linear regression that works much better than the regular one. It even avoid that the normal equation is non-reversible. The calculus is the same, but we add an extra term to the cost function.	To calculate the gradient descent, one must actualize the value of theta 0 and of others thetas, since the added sum takes from indexes 1 to n. The value of theta 0 is known as bias.

\begin{equation}
J(\theta) = \frac{1}{2m} \sum_{n=1}^{m} (h(x^{(i)})-y^{(i)})^{2} + \lambda\sum_{n=1}^{n} \theta_{j}^{2}
\end{equation}

Cost Function in logistic regression

\begin{equation}
J(\theta) = \frac{1}{m} \sum_{n=1}^{m} [-y^{(i)}}\log(h(x^{(i)}))-(1-y^{(i)})\log(1-h(x^{(i)})]
\end{equation}

### 2019-03-24 Rapport/TG_ITA/Bibliographic_analysis/General_research.tex
Assigment week 2

\subsection{Introduction to digital communication}

@@

>>>>

\subsection{Introduction to digital communication book}

@@

	 digital transmission, the number of bit errors is the number of received bits of a data stream over a communication channel that have been altered due to noise, interference, distortion or bit synchronization errors.
	 bit error rate (BER) is the number of bit errors per unit time.
	 The bit error ratio (also BER) is the number of bit errors divided by the total number of transferred bits during a studied time interval. 
	  bit error probability pe is the expectation value of the bit error ratio. The bit error ratio can be considered as an approximate estimate of the bit error probability. This estimate is accurate for a long time interval and a high number of bit errors.

	\subsubsection{Chapter 2 - Coding for discrete sources}
